A Cross-Benchmark Comparison of Learning to Rank Methods

### 2014-05-19 cikm_paper/paper.tex
werk

In recent years, several learning to rank benchmark datasets have been proposed with the aim of enabling comparison of the performance of different learning to rank methods. Well-known benchmark datasets in the learning to rank field include the \emph{Yahoo! Learning to Rank Challenge} dataset \cite{Chapelle2011a}, the Yandex Internet Mathematics competition\footnote{http://imat-relpred.yandex.ru/en/}, the LETOR dataset \cite{Qin2010}, and LETOR's successor the MSLR (Microsoft Learning to Rank) datasets.\\

No agreement exists between authors in the learning to rank field on the benchmark sets used for model evaluation. Comparing ranking performance of learning to rank methods is largely hindered by this lack of a \emph{de facto} standard way of benchmarking new models.

Several studies make a small start in considering learning to rank methods performance over multiple benchmark datasets. Gomes et al. \cite{Gomes2013} analysed ranking accuracy of a set of models on both LETOR 3.0 and LETOR 4.0. Busa-Fekete et al. \cite{Busa-Fekete2013} compared the accuracy of a small set of models over the LETOR 4.0 datasets, both MSLR datasets, both Yahoo! Learning to Rank Challenge datasets and one of the datasets from LETOR 3.0.\\

To our knowledge, no structured meta-analysis on ranking accuracy has been conducted where evaluation results on several benchmark collections are taken into account. In this paper we will perform a meta-analysis with the aim of comparing the ranking accuracy of learning to rank methods.

\section{Collecting Evaluation Results}

\subsection{Evaluation Results Collection Methodology}
\label{sec:collecting_evaluation_results}
With a literature review we will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}\itemsep0em
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics Competition 2009
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

\begin{table}[!h]
\begin{tabular}{p{3.2cm}|l|p{1.8cm}}
Benchmark & Paper & \# of forward references \\
\hline
LETOR 1.0 \& 2.0 & Liu et al. \cite{Liu2007b} & 307\\
LETOR 3.0 & Qin et al. \cite{Qin2010} & 105\\
Yahoo! Learning to Rank Challenge & Chapelle et al. \cite{Chapelle2011a} & 102\\
AOL dataset & Pass et al. \cite{Pass2006} & 339\\
WCL2R & Alc{\^a}ntara et al. \cite{Alcantara2010} & 2\\
\end{tabular}
\caption{Forward references of learning to rank benchmark papers}
\label{tbl:ltr_benchmark_forref}
\end{table}

@@

\begin{table}[!h]
\begin{tabular}{p{4.2cm}|p{2.5cm}}
Benchmark & Google scholar search results \\
\hline
LETOR 4.0 & 75 results \\
MSLR-web10k & 16 results \\
MSLR-web30k & 15 results \\
Yandex Internet Mathematics Competition & 1 result \\ 
\end{tabular}
\caption{Google scholar search results for learning to rank benchmarks}
\label{tbl:ltr_benchmark_searchres}
\end{table}

\subsection{Comparison Methodology of Learning to Rank Methods}
The LETOR 3.0 paper \cite{Qin2010} states that it may differ between datasets what the most accurate ranking methods are. To evaluate the overall performance of learning to rank methods over the multiple datasets in the LETOR 3.0 collections, Qin et al. \cite{Qin2010} proposed a measure called \emph{winning number} as the number of other algorithms that an algorithm can beat over the set of datasets. Formally the winning number measure is defined as\\

\section{Results \& Discussion}
\subsection{Collection of Evaluation Results}
Table \ref{tab:ltr_methods_used} gives an overview of the learning to rank methods for which evaluation results were found for one or more of the benchmark datasets listed in section~\ref{sec:collecting_evaluation_results} through the literature review process also described in section~\ref{sec:collecting_evaluation_results}. Occurrences of L2, L3 and L4 in Table \ref{tab:ltr_methods_used} imply that these algorithms are evaluated as official LETOR 2.0, LETOR 3.0 and LETOR 4.0 baselines respectively.\\

@@

\begin{tabular}{|l|l|l||l|l|l|}
Method & Described & Evaluated & Method & Described & Evaluated \\
\hline 

@@

\subsection{Comparison of Learning to Rank models}
The following subsections provide the performance of learning to rank methods in terms of Normalised Winning Number for NDCG@3, NDCG@5, NDCG@10 and MAP. Performance of the learning to rank methods is plotted with Normalised Winning Number on the vertical axis and the number of datasets on which the method has been evaluated on the horizontal axis. The further to the right, the more certain we can be about the performance of the learning to rank method. The methods for which it holds that there is no other method that has 1) a higher Normalised Winning Number and 2) a higher number datasets evaluated, are identified as the best performing methods and are labelled with the name of the method.

\subsubsection{NDCG@3}
Figure \ref{fig:normalised_winning_number_ndcg3} shows the performance of learning to rank methods for the NDCG@3 metric. Table \ref{tab:raw_data_norm_winnum_ndcg3} in Appendix \ref{app:norm_winnum_ndcg3} provides the raw Normalised Winning Number data for the learning to rank methods for which NDCG@3 evaluation results were available.\\

\begin{figure*}[!htp]
\includegraphics[scale=0.285]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of learning to rank methods}
\label{fig:normalised_winning_number_ndcg3}
\end{figure*}

@@

\subsubsection{NDCG@5}
Figure \ref{fig:normalised_winning_number_ndcg5} shows the performance of learning to rank methods for the NDCG@5 metric. Table \ref{tab:raw_data_norm_winnum_ndcg5} in Appendix \ref{app:norm_winnum_ndcg5} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure*}[!htp]
\includegraphics[scale=0.285]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of learning to rank methods}
\label{fig:normalised_winning_number_ndcg5}
\end{figure*}

@@

\subsubsection{NDCG@10}
Figure \ref{fig:normalised_winning_number_ndcg10} shows the performance of learning to rank methods for the NDCG@10 metric. Table \ref{tab:raw_data_norm_winnum_ndcg10} in Appendix \ref{app:norm_winnum_ndcg10} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure*}
\includegraphics[scale=0.285]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of learning to rank methods}
\label{fig:normalised_winning_number_ndcg10}
\end{figure*}

@@

\subsubsection{MAP}
Figure \ref{fig:normalised_winning_number_map} shows the performance of learning to rank methods for the MAP metric. Table \ref{tab:raw_data_norm_winnum_map} in Appendix \ref{app:norm_winnum_map} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure*}
\includegraphics[scale=0.285]{gfx/map_winnum}
\caption{MAP comparison of learning to rank methods}
\label{fig:normalised_winning_number_map}
\end{figure*}

@@

\subsubsection{Cross-metric}
Figure \ref{fig:normalised_winning_number_all} shows the Normalised Winning Number as function of Ideal Winning Number for the methods described in Table \ref{tab:ltr_methods_used}. Table \ref{tab:raw_data_norm_winnum_all} in Appendix \ref{app:norm_winnum_all} provide the raw data plotted in Figure \ref{fig:normalised_winning_number_all}.\\

@@

& \multicolumn{2}{p{0.5cm}}{NDCG@3} & \phantom{a} 

>>>>

In recent years, several learning to rank benchmark datasets have been proposed with the aim of enabling comparison of the performance of different learning to rank methods. Well-known benchmark datasets in the learning to rank field include the \emph{Yahoo! Learning to Rank Challenge} dataset \cite{Chapelle2011a}, the \emph{Yandex Internet Mathematics 2009} contest \footnote{http://imat2009.yandex.ru/en}, the LETOR dataset \cite{Qin2010}, and the MSLR (Microsoft Learning to Rank) datasets \footnote{http://research.microsoft.com/en-us/projects/mslr/}.\\

No agreement exists between authors in the learning to rank field on which benchmark set(s) to use for model evaluation. Comparing ranking performance of learning to rank methods is largely hindered by this lack of a \emph{de facto} standard way of benchmarking new models.\\

Gomes et al. \cite{Gomes2013} analysed ranking accuracy of a set of models on both LETOR 3.0 and LETOR 4.0. Busa-Fekete et al. \cite{Busa-Fekete2013} compared the accuracy of a small set of models over the LETOR 4.0 datasets, both MSLR datasets, both Yahoo! Learning to Rank Challenge datasets and one of the datasets from LETOR 3.0. Both studies did not aim to be complete in benchmark datasets and learning to rank methods included in their comparisons. To our knowledge, no structured meta-analysis on ranking accuracy has been conducted where evaluation results on several benchmark collections are taken into account. In this paper we will perform a meta-analysis with the aim of comparing the ranking accuracy of learning to rank methods. The paper will describe two stages in the meta-analysis process: 1) collection of evaluation results, and 2) comparison of learning to rank methods.

\section{Collecting Evaluation Results}
\label{sec:collecting_evaluation_results}
Through a literature review we will collect evaluation results on the datasets/collections. The following list presents an overview of the benchmark collections taken into account in the meta-analysis:
\begin{itemize}\itemsep0em
\item LETOR 2.0
\item LETOR 3.0
\item LETOR 4.0
\item Yahoo! Learning to Rank Challenge
\item Yandex Internet Mathematics 2009 contest
\item MSLR-web10/30k
\item WCL2R
\item AOL
\end{itemize}

@@

\begin{table}[!h]
\begin{tabular}{p{3.2cm}lp{1.8cm}}\toprule
Benchmark & Paper & \# of forward references \\
\midrule
LETOR 1.0 \& 2.0 & Liu et al. \cite{Liu2007b} & 307\\
LETOR 3.0 & Qin et al. \cite{Qin2010} & 105\\
Yahoo! Learning to Rank Challenge & Chapelle et al. \cite{Chapelle2011a} & 102\\
AOL dataset & Pass et al. \cite{Pass2006} & 339\\
WCL2R & Alc{\^a}ntara et al. \cite{Alcantara2010} & 2\\
\bottomrule
\end{tabular}
\caption{Forward references of learning to rank benchmark papers}
\label{tbl:ltr_benchmark_forref}
\end{table}

@@

\begin{table}[!h]
\begin{tabular}{p{4.2cm}p{2.5cm}}\toprule
Benchmark & Google scholar search results \\
\midrule
LETOR 4.0 & 75 results \\
MSLR-web10k & 16 results \\
MSLR-web30k & 15 results \\
Yandex Internet Mathematics & 3 results \\
\bottomrule
\end{tabular}
\caption{Google scholar search results for learning to rank benchmarks}
\label{tbl:ltr_benchmark_searchres}
\end{table}

\subsection{Literature selection}
Table \ref{tab:ltr_methods_used} gives an overview of the learning to rank methods for which evaluation results were found for one or more of the benchmark datasets listed in section~\ref{sec:collecting_evaluation_results} through the literature review process also described in section~\ref{sec:collecting_evaluation_results}. Occurrences of L2, L3 and L4 in Table \ref{tab:ltr_methods_used} imply that these algorithms are evaluated as official LETOR 2.0, LETOR 3.0 and LETOR 4.0 baselines respectively.\\

@@

\begin{tabular}{lll|lll}\toprule
Method & Described in & Evaluated in & Method & Described in & Evaluated in\\
\midrule

@@

\section{A Methodology for Comparing Learning to Rank Methods Cross-Benchmark}
The LETOR 3.0 paper \cite{Qin2010} states that it may differ between datasets what the most accurate ranking methods are. To evaluate the overall performance of learning to rank methods over the multiple datasets in the LETOR 3.0 collections, Qin et al. \cite{Qin2010} proposed a measure called \emph{winning number} as the number of other algorithms that an algorithm can beat over the set of datasets. Formally the winning number measure is defined as\\

\section{Results of Learning to Rank Comparison}
The following subsections provide the performance of learning to rank methods in terms of Normalised Winning Number for NDCG@3, NDCG@5, NDCG@10 and MAP. Performance of the learning to rank methods is plotted with Normalised Winning Number on the vertical axis and the number of datasets on which the method has been evaluated on the horizontal axis. The further to the right, the more certain we can be about the performance of the learning to rank method. The methods for which it holds that there is no other method that has 1) a higher Normalised Winning Number and 2) a higher number datasets evaluated, are identified as the best performing methods and are labelled with the name of the method.

\subsection{NDCG@3}
Figure \ref{fig:normalised_winning_number_ndcg3} shows the performance of learning to rank methods for the NDCG@3 metric. Table \ref{tab:raw_data_norm_winnum_ndcg3} in Appendix \ref{app:norm_winnum_ndcg3} provides the raw Normalised Winning Number data for the learning to rank methods for which NDCG@3 evaluation results were available.\\

\begin{figure}[!h]
\includegraphics[scale=0.285]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of learning to rank methods}
\label{fig:normalised_winning_number_ndcg3}
\end{figure}

@@

\subsection{NDCG@5}
Figure \ref{fig:normalised_winning_number_ndcg5} shows the performance of learning to rank methods for the NDCG@5 metric. Table \ref{tab:raw_data_norm_winnum_ndcg5} in Appendix \ref{app:norm_winnum_ndcg5} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure}[!h]
\includegraphics[scale=0.285]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of learning to rank methods}
\label{fig:normalised_winning_number_ndcg5}
\end{figure}

@@

\subsection{NDCG@10}
Figure \ref{fig:normalised_winning_number_ndcg10} shows the performance of learning to rank methods for the NDCG@10 metric. Table \ref{tab:raw_data_norm_winnum_ndcg10} in Appendix \ref{app:norm_winnum_ndcg10} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure}[!h]
\includegraphics[scale=0.285]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of learning to rank methods}
\label{fig:normalised_winning_number_ndcg10}
\end{figure}

@@

\subsection{MAP}
Figure \ref{fig:normalised_winning_number_map} shows the performance of learning to rank methods for the MAP metric. Table \ref{tab:raw_data_norm_winnum_map} in Appendix \ref{app:norm_winnum_map} provides the raw Normalised Winning Number data for the learning to rank methods.\\

\begin{figure}[!h]
\includegraphics[scale=0.285]{gfx/map_winnum}
\caption{MAP comparison of learning to rank methods}
\label{fig:normalised_winning_number_map}
\end{figure}

@@

\subsection{Cross-Metric}
Figure \ref{fig:normalised_winning_number_all} shows the Normalised Winning Number as function of Ideal Winning Number for the methods described in Table \ref{tab:ltr_methods_used}. Table \ref{tab:raw_data_norm_winnum_all} in Appendix \ref{app:norm_winnum_all} provide the raw data plotted in Figure \ref{fig:normalised_winning_number_all}.\\

@@

& \multicolumn{2}{c}{NDCG@3} & \phantom{a} 
